\vspace{2cm} \LARGE \bf Seasonal influenza circulation patterns and projections for 2017-2018

### 2017-09-20 auspice/reports/tex/feb-2017.tex
Fix figure references in Feb 2017 report

\begin{figure}[H]
	\centering
	\includegraphics[width=0.75\textwidth]{../figures/feb-2017/h3n2_frequencies.pdf}
	\caption{\textbf{Frequency trajectories of 3c2.a subclades.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Feb 1 2017.
	}
	\label{H3N2_mutations}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\textwidth]{../figures/feb-2017/h1n1pdm_frequencies.pdf}
	\caption{\textbf{Frequency trajectories of 6b.1 subclades.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Feb 1 2017.
	}
	\label{H1N1pdm_mutations}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{../figures/feb-2017/vic_frequencies.pdf}
	\caption{\textbf{Frequency trajectories of B/Vic variants.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Feb 1 2017.
	}
	\label{Vic_mutations}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{../figures/feb-2017/yam_frequencies.pdf}
	\caption{\textbf{Frequency trajectories of B/Yam variants.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Feb 1 2017.
	}
	\label{Yam_mutations}
\end{figure}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=0.75\textwidth]{../figures/feb-2017/h3n2_frequencies.png}
	\caption{\textbf{Frequency trajectories of 3c2.a subclades.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Feb 1 2017.
	}
	\label{H3N2_mutations}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\textwidth]{../figures/feb-2017/h1n1pdm_frequencies.png}
	\caption{\textbf{Frequency trajectories of 6b.1 subclades.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Feb 1 2017.
	}
	\label{H1N1pdm_mutations}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{../figures/feb-2017/vic_frequencies.png}
	\caption{\textbf{Frequency trajectories of B/Vic variants.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Feb 1 2017.
	}
	\label{Vic_mutations}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{../figures/feb-2017/yam_frequencies.png}
	\caption{\textbf{Frequency trajectories of B/Yam variants.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Feb 1 2017.
	}
	\label{Yam_mutations}
\end{figure}
